# Energy Services and Intensity

## Energy Service Shares
### Passenger
#### Transport mode w/o bunkers
```{r}
items <- c(
    "ES|Transport|Pass|Aviation|Domestic|Share w/o bunkers",
    "ES|Transport|Pass|Rail|non-HSR|Share w/o bunkers",
    "ES|Transport|Pass|Rail|HSR|Share w/o bunkers",
    "ES|Transport|Pass|Road|Bus|Share w/o bunkers",
    "ES|Transport|Pass|Road|LDV|Share w/o bunkers",
    "ES|Transport|Pass|Road|Non-Motorized|Walking|Share w/o bunkers",
    "ES|Transport|Pass|Road|Non-Motorized|Cycling|Share w/o bunkers"
  )

showAreaAndBarPlots(data, items)
```

#### Transport mode with bunkers
```{r}
items <- c(
    "ES|Transport|Pass|Aviation|International|Share",
    "ES|Transport|Pass|Aviation|Domestic|Share",
    "ES|Transport|Pass|Rail|non-HSR|Share",
    "ES|Transport|Pass|Rail|HSR|Share",
    "ES|Transport|Pass|Road|Bus|Share",
    "ES|Transport|Pass|Road|LDV|Share",
    "ES|Transport|Pass|Road|Non-Motorized|Walking|Share",
    "ES|Transport|Pass|Road|Non-Motorized|Cycling|Share"
  )

showAreaAndBarPlots(data, items)
```

#### LDV 4-Wheelers by vehicle size
```{r}
items <- c(
       "ES|Transport|Pass|Road|LDV|Large|Share",
       "ES|Transport|Pass|Road|LDV|Medium|Share",
       "ES|Transport|Pass|Road|LDV|SUV|Share",
       "ES|Transport|Pass|Road|LDV|Mini|Share",
       "ES|Transport|Pass|Road|LDV|Small|Share",
       "ES|Transport|Pass|Road|LDV|Van|Share"
  )

showAreaAndBarPlots(data, items)
```

### Freight
#### Transport mode w/o bunkers
```{r}
items <- c(
       "ES|Transport|Freight|Road|Share w/o bunkers",
       "ES|Transport|Freight|Rail|Share w/o bunkers",
       "ES|Transport|Freight|Navigation|Share w/o bunkers"
  )

showAreaAndBarPlots(data, items)
```
#### Transport mode with bunkers
```{r}
items <- c(
       "ES|Transport|Freight|Road|Share w/o bunkers",
       "ES|Transport|Freight|Rail|Share w/o bunkers",
       "ES|Transport|Freight|Navigation|Share w/o bunkers"
  )

showAreaAndBarPlots(data, items)
```
### Passenger LDV 4-Wheelers by vehicle technology

### Passenger LDV 2-Wheelers by technology

### Freight by vehicle type

### Freight Trucks by vehicle size

### Freight Trucks by technology

## Energy Service line plots
### Passenger
### Freight

## Energy Service Shares by transport mode
### Passenger
### Freight


## Energy Services Passenger per Capita
## Energy Services Passenger per GDP

## Energy Intensity 
### Passenger LDV|BEV
### Passenger LDV|FCEV
### Passenger LDV|Liquids
### Passenger Bus|BEV
### Passenger Bus|FCEV
### Passenger Bus|Liquids
### Freight Trucks|BEV
### Freight Trucks|FCEV
### Freight Trucks|Liquids